Assessing the potential of Jacobian-free Newton-Krylov methods for cell-centred finite volume solid mechanics

### 2024-12-28 article.tex
Paper updates

\usepackage{graphicx}%
\usepackage{amsmath,amssymb,amsfonts,bm}%
\usepackage{multirow}
\usepackage{amsthm}%
%\usepackage{subcaption}
\usepackage{mathrsfs}%
\usepackage[title]{appendix}%
\usepackage{xcolor}%
\usepackage{textcomp}%
\usepackage{manyfoot}%
\usepackage{booktabs}%
%\usepackage{algorithm}%
%\usepackage{algorithmicx}%
\usepackage{algpseudocode}%
\usepackage{listings}%
\usepackage{bigints}
\usepackage{outlines}
\usepackage{geometry}
\usepackage{subfigure}
\usepackage{siunitx}
\usepackage{float}

@@

%%--------------------------------------------------------------------------------------------------------------------%%
\subsection{Testing the Accuracy and Order of Accuracy}
\label{sec:accuracy}
%%--------------------------------------------------------------------------------------------------------------------%%
This section solely focuses on assessing the accuracy and order of accuracy of the discretisation.
Assessment of the computational efficiency regarding time and memory requirements is left to the subsequent sections.

@@

\paragraph{Case 1: Order Verification via the Manufactured Solution Procedure}
The first test case consists of a $0.2 \times 0.2 \times 0.2$ m cube with linear elastic ($E = 200$ GPa, $\nu = 0.3$) properties.
A manufactured solution for displacement (Figure \ref{fig:mms_solution}) is employed of the form:
\begin{eqnarray}
	\bb{u} =
	\begin{pmatrix}
	a_x \sin(4\pi x) \sin(2\pi y) \sin(\pi z) \\
	a_y \sin(4 \pi x) \sin(2 \pi y) \sin(\pi z) \\
	a_z \sin(4 \pi x) \sin(2 \pi y) \sin(\pi z) 
	\end{pmatrix}
\end{eqnarray}
where $a_x = 2\times10^{-6}$ m, $a_y = 4\times10^{-6}$ m, and $a_z = 6\times10^{-6}$ m.
The Cartesian coordinates are given by $x$, $y$ and $z$.
The corresponding manufactured body force term is given in Appendix \ref{app:mms}.
%\begin{figure}[htbp]
%   \centering
%   \includegraphics[width=0.5\textwidth]{figures/mms_solution} 
%   \caption{Cut plane through the cube case geometry showing the magnitude of the manufactured displacement solution. The cut plane passes through the centre of the cube and has the unit normal $\bb{n} = (\sfrac{1}{\sqrt{3}} \quad \sfrac{1}{\sqrt{3}} \quad \sfrac{1}{\sqrt{3}})$.}
%   \label{fig:mms_solution}
%\end{figure}
\begin{figure}[htbp]
	\centering
	\subfigure[Magnitude of the manufactured displacement solution]
	{
		\label{fig:mms_solution}
   		\includegraphics[height=0.45\textwidth]{figures/mms_solution} 
   	}
	\subfigure[Polyhedral mesh with $1\,000$ cells]
	{
		\label{fig:mms_mesh}
   		\includegraphics[height=0.45\textwidth]{figures/mms_mesh}  
   	}
	\caption{A cut plane through the cube case geometry showing the magnitude of the manufactured displacement solution (left) and a polyhedral mesh (right). The cut plane passes through the centre of the cube and has the unit normal $\bb{n} = (\sfrac{1}{\sqrt{3}} \quad \sfrac{1}{\sqrt{3}} \quad \sfrac{1}{\sqrt{3}})$.}
	\label{fig:mms}
\end{figure}

The manufactured displacement solution is applied at the domain's boundaries, and inertial effects are neglected.
Three mesh types are examined: (i) hexahedra, (ii) tetrahedra, and (iii) regular polyhedra (Figure \ref{fig:mms_mesh}).
The hexahedral meshes are created using the OpenFOAM \texttt{blockMesh} utility, while the tetrahedral meshes are created using Gmsh \citep{geuzaine2009gmsh}.
To create the polyhedral meshes, the tetrahedra meshes are converted to their dual polyhedral representations using the OpenFOAM \texttt{polyDualMesh} utility.
Starting from an initial mesh spacing of $0.04$ m, six meshes are created by successively halving the spacing.
The cell numbers for the hexahedral and polyhedral meshes are 125, $1\,000$, $8\,000$, $64\,000$, $512\,000$, and $4\,096\,000$, while the tetrahedral mesh cell counts are 384, $4\,374$, $41\,154$, $355\,914$, $2\,958\,234$, and $24\,118\,074$.
For the same average cell width, the cell counts show that the tetrahedral meshes have larger cell counts by a factor of 3 to 6.

Figure \ref{fig:mms_disp_accuracy}(a) shows the displacement magnitude discretisation errors ($L_2$ and $L_\infty$) as a function of the average cell width for all three mesh types (hexahedral, tetrahedral and polyhedral), while Figure \ref{fig:mms_disp_accuracy}(b) shows the corresponding order of accuracy plots.
For ease of interpretation, the symbol shapes in the figures have been chosen to correspond to the cell shapes: a square for hexahedra, a triangle for tetrahedra and a pentagon for polyhedra.
The maximum ($L_\infty$) and average ($L_2$) discretisation errors are seen to reduce at an approximately second-order rate for all mesh types, except for the $L_2$ error on the hexahedral meshes, which is approximately 2.3 on the finest grid.
%where, interestingly, the errors are, on average, smaller on the polyhedral meshes.
%The reason for this is unclear but may be due to the stencil of the structured polyhedra being more isotropic and containing close neighbours.
\begin{figure}[htbp]
	\centering
	\subfigure[Displacement magnitude discretisation errors]
	{
   		\includegraphics[width=0.45\textwidth]{figures/mms_dispErrors} 
   	}
	\subfigure[Displacement discretisation error order of accuracy]
	{
   		\includegraphics[width=0.45\textwidth]{figures/mms_disp_orderOfAccuracy}  
   	}
	\caption{Manufactured solution cube case: the accuracy and order of accuracy for displacement magnitude}
	\label{fig:mms_disp_accuracy}
\end{figure}

The predicted $\sigma_{xx}$ stress distribution for a hexahedral mesh with $512\,000$ cells is shown in Figure \ref{fig:mms_stress}(a).
The corresponding cell-wise $\sigma_{xx}$ error distribution is shown in Figure \ref{fig:mms_stress}(b).
The errors of greatest magnitude ($43$ kPa) occur at the boundaries, corresponding to where the local truncation error is higher due to the use of one-sided differencing.
\begin{figure}[htbp]
	\centering
	\subfigure[Predicted $\sigma_{xx}$ stress distribution]
	{
		\label{fig:mms_sxx}
   		\includegraphics[height=0.35\textwidth]{figures/mms_sxx} 
   	}
	\subfigure[Cell-wise $\sigma_{xx}$ error distribution]
	{
		\label{fig:mms_sxx_diff}
   		\includegraphics[height=0.35\textwidth]{figures/mms_sxx_diff}  
   	}
	\caption{Manufactured solution cube case: the predicted $\sigma_{xx}$ stress distribution on a cut-plane for the hexahedral mesh with $512\,000$ cells (left).}
	\label{fig:mms_stress}
\end{figure}
The discretisation errors in the stress magnitude are shown in Figure \ref{fig:mms_stress_accuracy}(a), and the order of accuracy in Figure \ref{fig:mms_stress_accuracy}(b).
The order of accuracy for the average ($L_2$) stress error is seen to be approximately 1.5 for the hexahedral and polyhedral meshes.
In contrast, the average stress error order for the tetrahedral meshes is 1.
Similarly, the maximum ($L_\infty$) stress order of accuracy is seen to approach 1 for all three mesh types.
\begin{figure}[htbp]
	\centering
	\subfigure[Stress magnitude discretisation errors]
	{
   		\includegraphics[width=0.45\textwidth]{figures/mms_stressErrors} 
   	}
	\subfigure[Stress discretisation error order of accuracy]
	{
   		\includegraphics[width=0.45\textwidth]{figures/mms_stress_orderOfAccuracy}  
   	}
	\caption{Manufactured solution cube case: the accuracy and order of accuracy for stress magnitude}
	\label{fig:mms_stress_accuracy}
\end{figure}

The presented results have been generated using the Jacobian-free Newton-Raphson solution algorithm; however, minimal differences were seen when using the segregated solution algorithm, and hence, the segregated results are not shown.
%This section assesses the order of accuracy of the discretisation using a manufactured solution on a cube domain (case 1).
%A secondary purpose is to demonstrate that the choice of solution algorithm (Jacobian-free Newton-Krylov vs segregated) does not affect the predictions, assuming iteration errors are small.

% Note: this is PETSc segregated so discretisation is exactly the same; OF segregated will be slightly different as boundary gradients are different
% \hl{check - maybe one comparison graph}.
%\hl{Seg and JFNK are the same when including boundary values but this causes a problem for the poly grid}

@@

@@

The predictions for the equivalent (von Mises) stress along the line $r = \sqrt{x^2 + y^2} = 2.1$ m, $z = 0.3$ m is shown in Figure \ref{fig:elliptic_plate_sigmaEq}.
The results from the finest grid in \citet{Demirdzic1997a} are given for comparison, where good agreement is seen;
the small offset between the finest mesh predictions and those from \citet{Demirdzic1997a} are likely due to errors introduced when extracting the \citet{Demirdzic1997a} results using WebPlotDigitizer \citep{WebPlotDigitizer}.
The sample values have been calculated by generating 40 uniformly spaced angles between 0 and $\frac{\pi}{2}$ along the line, finding the cell of each sampled point, and extrapolating from the cell-centred value using the field gradient.
\begin{figure}[htbp]
   \centering
   %\includegraphics[width=0.5\textwidth]{figures/elliptic_plate_sigmaEq_line.pdf} 
	\subfigure[Equivalent stress distribution for the mesh with $2\,438\,242$ cells. The deformation is scaled by $1\,000$ and a translucent line indicates the outline of the undeformed geometry]
	{
		\includegraphics[width=0.45\textwidth]{figures/elliptic_plate_sigmaEq}  
	}
	\subfigure[Equivalent stress along the line $r = 2.1$, $z = 0.3$ m]
	{
		\includegraphics[width=0.45\textwidth]{figures/elliptic_plate_sigmaEq_line.pdf} 
	}
   \caption{Equivalent (von Mises) stress distribution in the elliptic plate}
   \label{fig:elliptic_plate_sigmaEq}
\end{figure}

\paragraph{Case 3: Narrow T-section component under tension}
This case, proposed by \citet{Demirdzic1997a}, consists of a narrow engineering component with a T cross-section (Figure \ref{fig:narrowTmember}).
The case is 3-D, static, with linear elastic material behaviour.
Symmetry allows one-quarter of the geometry to be simulated.
A constant negative pressure of 1 MPa is applied to the lower surface, and the upper left surface is fully clamped.
The Young’s modulus is $E = 210$ GPa, and Poisson’s ratio is $\nu = 0.3$.
A radius $5$ mm hole is located at the expected stress concentration.
%\begin{figure}[htbp]
%   \centering
%   \includegraphics[width=0.4\textwidth]{figures/narrowTmember-geometry.pdf} 
%   \caption{Inflation of an idealised ventricle case geometry, mesh and loading conditions}
%   \label{fig:narrowTmember}
%\end{figure}
\begin{figure}[htbp]
	\centering
	\subfigure[Case geometry (considered quarter geometry)]
	{
		\label{fig:narrowTmember_geometry}
   		\includegraphics[height=0.4\textwidth]{figures/narrowTmember-geometry} 
   	}
   	\qquad
	\subfigure[Mesh with 624 cells]
	{
		\label{fig:narrowTmember_mesh}
   		\includegraphics[height=0.4\textwidth]{figures/narrowTmember-mesh}  
   	}
	\caption{Narrow T-section component under tension: geometry and mesh}
	\label{fig:narrowTmember}
\end{figure}

@@

The predicted equivalent (von Mises) stress distribution on the $z = 0$ plane is shown in Figure \ref{fig:narrowTmember_sigmaEq}(a), where a stress concentration is apparent near the hole.
The equivalent stress along the line $r = 1.5R$, $z = 0$ is shown for the different meshes in Figure \ref{fig:narrowTmember_sigmaEq}(b), where $R$ is the hole radius.
The predictions are seen converge to the results reported in \citet{Demirdzic1997a}.
Similarly to the elliptic plate case, the sample values have been to by generating 30 uniformly spaced angles between $-\frac{\pi}{2}$ and $-\pi$ along the line, finding the cell of each sampled point, and extrapolating from the cell-centred value using the field gradient.
\begin{figure}[htbp]
   \centering
	\subfigure[Equivalent stress distribution for the mesh with $2\,555\,904$ cells on the $z = 0$ m plane]
	{
		\includegraphics[height=0.32\textwidth]{figures/narrowTmember_sigmaEq}  
	}
	\subfigure[Equivalent stress along the line $r = 1.5R$, $z = 0$ m]
	{
		\includegraphics[height=0.32\textwidth]{figures/narrowTmember_sigmaEq_line.pdf} 
	}
   \caption{Equivalent (von Mises) stress distribution in the narrow T-section component under tension}
   \label{fig:narrowTmember_sigmaEq}
\end{figure}

\paragraph{Case 4: Inflation of an idealised ventricle}
Inflation of an idealised ventricle (Figure \ref{fig:ventricle}) was proposed by \citet{Land2015} as a benchmark problem for cardiac mechanics software.
The case is 3-D, static, with finite hyperelastic strains.
The initial geometry is defined as a truncated ellipsoid:
\begin{eqnarray}
	x = r_s \sin(u) \cos(v), \quad
	y = r_s \sin(u) \sin(v), \quad
	z = r_l \cos(u)
\end{eqnarray}
where on the inner (endocardial) surface $r_s =7$ mm, $r_l = 17$ mm, $u \in \left[-\pi, -\arccos \left( \frac{5}{17} \right) \right]$ and $v \in \left[-\pi, \pi \right]$, while on the outer (epicardial) surface $r_s =10$ mm, $r_l = 20$ mm, $u \in \left[-\pi, -\arccos \left( \frac{5}{20} \right) \right]$ and $v \in \left[-\pi, \pi \right]$.
The base plane $z = 5$ mm is implicitly defined by the ranges for $u$.
%Constitutive parameters: isotropic, 
The hyperelastic material behaviour is described by the transversely isotropic constitutive proposed by \citet{Guccione1995} law, where the parameters are $C = 10$ kPa, $b_f = b_t = b_{fs} = 1$.
The benchmark specifies an incompressible material; in the current work, incompressibility is enforced weakly using a penalty approach, where the bulk modulus parameter is chosen to be two orders of magnitude greater ($\kappa = 1000$ kPa) than the greatest shear modulus parameter.
The chosen parameters produce isotropic behaviour.
A pressure of 10 kPa is applied to the inner surface, and the base plane is fixed.
The geometry is meshed using a structured approach and is predominantly composed of hexahedra, with prism cells forming the apex.
The OpenFOAM utilities \texttt{blockMesh} and \texttt{extrudeMesh} are used to create the meshes.
Four successively refined meshes are examined: $1\,620$ (shown in Figure \ref{fig:ventricle}(a)), $12\,960$, $103\,680$, and $829\,440$ cells.
The case can be simulated as 2-D axisymmetric but is simulated here using the full 3-D geometry.
%Figure \ref{fig:ventricle} shows the mesh with 1,620 cells (1,512 hexahedra and 108 prisms).
\begin{figure}[htbp]
   \centering
%   \includegraphics[width=0.4\textwidth]{figures/ventricle} 
	\subfigure[Ventricle undeformed geometry, showing the mesh with 1,620 cells]
	{
		\includegraphics[height=0.46\textwidth]{figures/ventricle} 
	}
	\subfigure[Cross-section showing the equivalent (von Mises) stress distribution for the mesh with 829,440 cells]
	{
		\includegraphics[height=0.48\textwidth]{figures/ventricle_sigmaEq}
	}
   \caption{Idealised ventricle case}
   \label{fig:ventricle}
\end{figure}

>>>>

\usepackage{graphicx}%
\usepackage{amsmath,amssymb,amsfonts,bm}%
\usepackage{multirow}
\usepackage{amsthm}%
%\usepackage{subcaption}
\usepackage{mathrsfs}%
\usepackage[title]{appendix}%
\usepackage{xcolor}%
\usepackage{textcomp}%
\usepackage{manyfoot}%
\usepackage{booktabs}%
%\usepackage{algorithm}%
%\usepackage{algorithmicx}%
\usepackage{algpseudocode}%
\usepackage{listings}%
\usepackage{bigints}
\usepackage{outlines}
\usepackage{geometry}
\usepackage{subfigure}
\usepackage{siunitx}
\usepackage{float}
\usepackage{comment}

@@

%%--------------------------------------------------------------------------------------------------------------------%%
\subsection{Testing the Accuracy and Order of Accuracy}
\label{sec:accuracy}
%%--------------------------------------------------------------------------------------------------------------------%%
This section solely focuses on assessing the accuracy and order of accuracy of the discretisation.
Assessment of the computational efficiency regarding time and memory requirements is left to the subsequent sections.
In all cases where convergence is achieved, the differences between the Jacobian-free Newton-Raphson and segregated approaches are minimal;
%No difference is seen in the predictions whether using the Jacobian-free Newton-Krylov or segregated approach, assuming convergence is achieved.
this is expected since both approaches use the same discretisation, and the solution tolerances have been chosen to ensure the iteration errors are small.
Consequently, the results presented below (Section \ref{sec:accuracy}) have been solely generated using the Jacobian-free Newton-Raphson solution algorithm, unless stated otherwise.

@@

\paragraph{Case 1: Order Verification via the Manufactured Solution Procedure}
The first test case consists of a $0.2 \times 0.2 \times 0.2$ m cube with linear elastic ($E = 200$ GPa, $\nu = 0.3$) properties.
A manufactured solution for displacement (Figure \ref{fig:mms_solution}) is employed of the form \citep{Mazzanti2024}
\begin{eqnarray}
	\bb{u} =
	\begin{pmatrix}
	a_x \sin(4\pi x) \sin(2\pi y) \sin(\pi z) \\
	a_y \sin(4 \pi x) \sin(2 \pi y) \sin(\pi z) \\
	a_z \sin(4 \pi x) \sin(2 \pi y) \sin(\pi z) 
	\end{pmatrix}
\end{eqnarray}
where $a_x = 2\,\mu$m, $a_y = 4\,\mu$m, and $a_z = 6\,\mu$m.
The Cartesian coordinates are given by $x$, $y$ and $z$.
The corresponding manufactured body force term ($\bb{f}_b$  in Equation \ref{eqn:momentum_lingeom}) is given in Appendix \ref{app:mms}.
%\begin{figure}[htbp]
%   \centering
%   \includegraphics[width=0.5\textwidth]{figures/mms_solution} 
%   \caption{Cut plane through the cube case geometry showing the magnitude of the manufactured displacement solution. The cut plane passes through the centre of the cube and has the unit normal $\bb{n} = (\sfrac{1}{\sqrt{3}} \quad \sfrac{1}{\sqrt{3}} \quad \sfrac{1}{\sqrt{3}})$.}
%   \label{fig:mms_solution}
%\end{figure}
\begin{figure}[htbp]
	\centering
	\subfigure[Magnitude of the manufactured displacement solution]
	{
		\label{fig:mms_solution}
   		\includegraphics[height=0.45\textwidth]{figures/mms_solution} 
   	}
	\subfigure[Regular polyhedral mesh with $1\,000$ cells]
	{
		\label{fig:mms_mesh}
   		\includegraphics[height=0.45\textwidth]{figures/mms_mesh}  
   	}
	\caption{A cut plane through the cube case geometry showing the magnitude of the manufactured displacement solution (left) and a polyhedral mesh (right). The cut plane passes through the centre of the cube and has the unit normal $\bb{n} = (\sfrac{1}{\sqrt{3}} \quad \sfrac{1}{\sqrt{3}} \quad \sfrac{1}{\sqrt{3}})$.}
	\label{fig:mms}
\end{figure}

The manufactured displacement solution is applied at the domain's boundaries, and inertial effects are neglected.
Three mesh types are examined:
%(i) \emph{regular} hexahedra, (ii) \emph{distorted} hexahedra, (iii) tetrahedra, and (iv) polyhedra (shown in Figure \ref{fig:mms_mesh}).
(i) hexahedra, (ii) tetrahedra, and (iii) polyhedra (shown in Figure \ref{fig:mms_mesh}).
The hexahedral meshes are created using the OpenFOAM \texttt{blockMesh} utility, while the tetrahedral meshes are created using Gmsh \citep{geuzaine2009gmsh}.
To create the polyhedral meshes, the tetrahedra meshes are converted to their dual polyhedral representations using the OpenFOAM \texttt{polyDualMesh} utility.
%The distorted hexahedral meshes are created by perturbing the points of the regular hexahedra by a random vector of magnitude less than 0.3 times the local minimum edge length.
%Points on the corners and edges of the cube domain are not moved, while the remaining boundary points are limited to slide along the boundary.
%During perturbation, if needed, the local point perturbation is iteratively reduced to ensure the local distorted cell volumes are not less than 10\% of their original volume and the maximum face non-orthogonality is less than $70^\circ$.
%Consequently, the meshes can be considered moderately distorted.
%Appendix \ref{app:meshes} includes images of all three cell types for both regular and distorted configurations.
Starting from an initial mesh spacing of $0.04$ m, six meshes of each type are created by successively halving the spacing.
The cell numbers for the hexahedral and polyhedral meshes are 125, $1\,000$, $8\,000$, $64\,000$, $512\,000$, and $4\,096\,000$, while the tetrahedral mesh cell counts are 384, $4\,374$, $41\,154$, $355\,914$, $2\,958\,234$, and $24\,118\,074$.
For the same average cell width, the cell counts show that the tetrahedral meshes have more cells by a factor of 3 to 6.
Table \ref{tab:mmsMesh} lists the average and maximum face non-orthogonality for the meshes of different cell types, where face non-orthogonality is defined as the angle made by the vector between the two adjacent cell centres across the common face and the face normal.
\begin{table}[htb]
    \centering
    \begin{tabular}{lll}
        \hline
        Cell type & Average & Maximum \\
        \hline
        Hexahedra & 0 &0  \\
        Tetrahedra & 32.71 & 35.26 \\
        Polyhedra & 30.65 & 38.45 \\
        \hline
    \end{tabular}
%    \begin{tabular}{l|cc|cc}
%        \hline
%        Cell type & \multicolumn{2}{c|}{Regular} & \multicolumn{2}{c}{Distorted} \\
%        & Average & Maximum & Average & Maximum \\
%        \hline
%        Hexahedra & 0 &0 & 13.10 & 52.51 \\
%        Tetrahedra & 32.73 & 35.26 & 34.83 & 69.96 \\
%        Polyhedra & 30.90 & 38.38 & 3 & 4 \\
%        \hline
%    \end{tabular}
    \caption{Average and maximum face non-orthogonality (in $^\circ$) for the meshes of different cell types and sizes}
    \label{tab:mmsMesh}
\end{table}

Figure \ref{fig:mms_disp_accuracy}(a) shows the displacement magnitude discretisation errors ($L_2$ and $L_\infty$) as a function of the average cell width for the three mesh types (hexahedral, tetrahedral and polyhedral), while Figure \ref{fig:mms_disp_accuracy}(b) shows the corresponding order of accuracy plots.
For ease of interpretation, the symbol shapes in the figures have been chosen to correspond to the cell shapes: a square for hexahedra, a triangle for tetrahedra and a pentagon for polyhedra.
The maximum ($L_\infty$) and average ($L_2$) displacement discretisation errors are seen to reduce at an approximately second-order rate for all mesh types, except for the $L_2$ error on the hexahedral meshes, which is approximately 2.3 on the finest grid.
%where, interestingly, the errors are, on average, smaller on the polyhedral meshes.
%The reason for this is unclear but may be due to the stencil of the structured polyhedra being more isotropic and containing close neighbours.
\begin{figure}[htbp]
	\centering
	\subfigure[Displacement magnitude discretisation errors]
	{
   		\includegraphics[width=0.45\textwidth]{figures/mms_dispErrors} 
   	}
	\subfigure[Displacement discretisation error order of accuracy]
	{
   		\includegraphics[width=0.45\textwidth]{figures/mms_disp_orderOfAccuracy}  
   	}
	\caption{Manufactured solution cube case: the accuracy and order of accuracy for displacement magnitude on the \emph{regular} meshes}
	\label{fig:mms_disp_accuracy}
\end{figure}

The predicted $\sigma_{xx}$ stress distribution for a hexahedral mesh with $512\,000$ cells is shown in Figure \ref{fig:mms_stress}(a).
The corresponding cell-wise $\sigma_{xx}$ error distribution is shown in Figure \ref{fig:mms_stress}(b).
The errors of greatest magnitude ($43$ kPa) occur at the boundaries, corresponding to where the local truncation error is higher. % due to the use of one-sided differencing.
\begin{figure}[htbp]
	\centering
	\subfigure[Predicted $\sigma_{xx}$ stress distribution]
	{
		\label{fig:mms_sxx}
   		\includegraphics[height=0.35\textwidth]{figures/mms_sxx} 
   	}
	\subfigure[Cell-wise $\sigma_{xx}$ error distribution]
	{
		\label{fig:mms_sxx_diff}
   		\includegraphics[height=0.35\textwidth]{figures/mms_sxx_diff}  
   	}
	\caption{Manufactured solution cube case: the predicted $\sigma_{xx}$ stress distribution on a cut-plane for the regular hexahedral mesh with $512\,000$ cells (left).}
	\label{fig:mms_stress}
\end{figure}
The discretisation errors in the stress magnitude as a function of cell size are shown in Figure \ref{fig:mms_stress_accuracy}(a), and the order of accuracy in Figure \ref{fig:mms_stress_accuracy}(b).
The order of accuracy for the average ($L_2$) stress error is seen to be approximately 1.5 for the hexahedral and polyhedral meshes.
In contrast, the average stress error order for the tetrahedral meshes is 1.
Similarly, the maximum ($L_\infty$) stress order of accuracy is seen to approach 1 for all three mesh types.
\begin{figure}[htbp]
	\centering
	\subfigure[Stress magnitude discretisation errors]
	{
   		\includegraphics[width=0.45\textwidth]{figures/mms_stressErrors} 
   	}
	\subfigure[Stress discretisation error order of accuracy]
	{
   		\includegraphics[width=0.45\textwidth]{figures/mms_stress_orderOfAccuracy}  
   	}
	\caption{Manufactured solution cube case: the accuracy and order of accuracy for stress magnitude}
	\label{fig:mms_stress_accuracy}
\end{figure}

%\hl{Distorted grids}

%%%%%%%%%%%%
\begin{comment}
%%%%%%%%%%%%

@@

%%%%%%%%%%%%
\end{comment}
%%%%%%%%%%%%

%%%%%%%%%%%%
\begin{comment}
%%%%%%%%%%%%

@@

The predictions for the equivalent (von Mises) stress along the line $r = \sqrt{x^2 + y^2} = 2.1$ m, $z = 0.3$ m is shown in Figure \ref{fig:elliptic_plate_sigmaEq}.
The results from the finest grid in \citet{Demirdzic1997a} are given for comparison, where good agreement is seen;
the small offset between the finest mesh predictions and those from \citet{Demirdzic1997a} are likely due to errors introduced when extracting the \citet{Demirdzic1997a} results using WebPlotDigitizer \citep{WebPlotDigitizer}.
The sample values have been calculated by generating 40 uniformly spaced angles between 0 and $\nicefrac{\pi}{2}$ along the line, finding the cell of each sampled point, and extrapolating from the cell-centred value using the field gradient.
\begin{figure}[htbp]
   \centering
   %\includegraphics[width=0.5\textwidth]{figures/elliptic_plate_sigmaEq_line.pdf} 
	\subfigure[Equivalent stress distribution for the mesh with $2\,438\,242$ cells. The deformation is scaled by $1\,000$ and a translucent line indicates the outline of the undeformed geometry]
	{
		\includegraphics[width=0.45\textwidth]{figures/elliptic_plate_sigmaEq}  
	}
	\subfigure[Equivalent stress along the line $r = 2.1$, $z = 0.3$ m]
	{
		\includegraphics[width=0.45\textwidth]{figures/elliptic_plate_sigmaEq_line.pdf} 
	}
   \caption{Equivalent (von Mises) stress distribution in the elliptic plate}
   \label{fig:elliptic_plate_sigmaEq}
\end{figure}

%%%%%%%%%%%%
\end{comment}
%%%%%%%%%%%%

\paragraph{Case 2: Narrow T-section component under tension}
This case, proposed by \citet{Demirdzic1997a}, consists of a narrow engineering component with a T cross-section (Figure \ref{fig:narrowTmember}).
The case is 3-D, static, with linear elastic material behaviour.
Symmetry allows one-quarter of the geometry to be simulated.
A constant negative pressure of 1 MPa is applied to the lower surface, and the upper left surface is fully clamped.
The Young’s modulus is $E = 210$ GPa, and Poisson’s ratio is $\nu = 0.3$.
A radius $5$ mm hole is located at the expected stress concentration.
%\begin{figure}[htbp]
%   \centering
%   \includegraphics[width=0.4\textwidth]{figures/narrowTmember-geometry.pdf} 
%   \caption{Inflation of an idealised ventricle case geometry, mesh and loading conditions}
%   \label{fig:narrowTmember}
%\end{figure}
\begin{figure}[htbp]
	\centering
	\subfigure[Case geometry (considered quarter geometry)]
	{
		\label{fig:narrowTmember_geometry}
   		\includegraphics[height=0.4\textwidth]{figures/narrowTmember-geometry} 
   	}
   	\qquad
	\subfigure[Mesh with 624 cells]
	{
		\label{fig:narrowTmember_mesh}
   		\includegraphics[height=0.4\textwidth]{figures/narrowTmember-mesh}  
   	}
	\caption{Narrow T-section component under tension: geometry and mesh}
	\label{fig:narrowTmember}
\end{figure}

@@

The predicted equivalent (von Mises) stress distribution on the $z = 0$ plane is shown in Figure \ref{fig:narrowTmember_sigmaEq}(a), where a stress concentration is apparent near the hole.
The equivalent stress along the line $r = 1.5R$, $z = 0$ is shown for the different meshes in Figure \ref{fig:narrowTmember_sigmaEq}(b), where $R$ is the hole radius.
%Similarly to the elliptic plate case, 
The stress values have been sampled at 30 uniformly spaced angles between $-\frac{\pi}{2}$ and $-\pi$ along the line $r = 1.5R$, $z = 0$, finding the cell of each sampled point, and extrapolating from the cell-centred value using the field gradient.
The predictions are seen converge to the results reported in \citet{Demirdzic1997a}.
\begin{figure}[htbp]
   \centering
	\subfigure[Equivalent stress distribution for the mesh with $2\,555\,904$ cells on the $z = 0$ m plane]
	{
		\includegraphics[height=0.32\textwidth]{figures/narrowTmember_sigmaEq}  
	}
	\subfigure[Equivalent stress along the line $r = 1.5R$, $z = 0$ m]
	{
		\includegraphics[height=0.32\textwidth]{figures/narrowTmember_sigmaEq_line.pdf} 
	}
   \caption{Equivalent (von Mises) stress distribution in the narrow T-section component under tension}
   \label{fig:narrowTmember_sigmaEq}
\end{figure}

\paragraph{Case 3: Inflation of an idealised ventricle}
Inflation of an idealised ventricle (Figure \ref{fig:ventricle}) was proposed by \citet{Land2015} as a benchmark problem for cardiac mechanics software.
The case is 3-D, static, with finite hyperelastic strains.
The initial geometry is defined as a truncated ellipsoid:
\begin{eqnarray}
	x = r_s \sin(u) \cos(v), \quad
	y = r_s \sin(u) \sin(v), \quad
	z = r_l \cos(u)
\end{eqnarray}
where on the inner (endocardial) surface $r_s =7$ mm, $r_l = 17$ mm, $u \in \left[-\pi, -\arccos \left( \frac{5}{17} \right) \right]$ and $v \in \left[-\pi, \pi \right]$, while on the outer (epicardial) surface $r_s =10$ mm, $r_l = 20$ mm, $u \in \left[-\pi, -\arccos \left( \frac{5}{20} \right) \right]$ and $v \in \left[-\pi, \pi \right]$.
The base plane $z = 5$ mm is implicitly defined by the ranges for $u$.
%Constitutive parameters: isotropic, 
The hyperelastic material behaviour is described by the transversely isotropic constitutive law proposed by \citet{Guccione1995} law, where the parameters are $C = 10$ kPa, $b_f = b_t = b_{fs} = 1$; the specified parameters produce isotropic behaviour.
The benchmark specifies an incompressible material; in the current work, incompressibility is enforced weakly using a penalty approach, where the bulk modulus parameter is chosen to be two orders of magnitude greater ($\kappa = 1000$ kPa) than the greatest shear modulus parameter.
A pressure of 10 kPa is applied to the inner surface, applied here over 100 equal load increments, and the base plane is fixed.
The geometry is meshed using a structured approach and is predominantly composed of hexahedra, with prism cells forming the apex.
The OpenFOAM utilities \texttt{blockMesh} and \texttt{extrudeMesh} are used to create the meshes.
Four successively refined meshes are examined: $1\,620$ (shown in Figure \ref{fig:ventricle}(a)), $12\,960$, $103\,680$, and $829\,440$ cells.
The case can be simulated as 2-D axisymmetric but is simulated here using the full 3-D geometry.
%Figure \ref{fig:ventricle} shows the mesh with 1,620 cells (1,512 hexahedra and 108 prisms).
\begin{figure}[htbp]
   \centering
%   \includegraphics[width=0.4\textwidth]{figures/ventricle} 
	\subfigure[Ventricle undeformed geometry, showing the mesh with 1,620 cells]
	{
		\includegraphics[height=0.46\textwidth]{figures/ventricle} 
	}
	\subfigure[Cross-section showing the equivalent (von Mises) stress distribution for the mesh with 829,440 cells]
	{
		\includegraphics[height=0.48\textwidth]{figures/ventricle_sigmaEq}
	}
   \caption{Idealised ventricle case}
   \label{fig:ventricle}
\end{figure}

The equivalent (von Mises) stress at full inflation is shown for the mesh with 829,440 cells in Figure \ref{fig:ventricle}(b), where the high stresses on the inner (endocardial) surface quickly drop off through the wall thickness towards the outer (endocardial) surface.
The predicted deformed configuration of the ventricle wall midline is shown in Figure \ref{fig:ventricle_accuracy}, where a side-by-side comparison is given with the round-robin benchmark results from \citet{Land2015}.
The predictions are seen to become quickly mesh-independent and fall within the benchmark ranges.
%The variation in the round-robin results may be explained by the sensitivity of the predictions to the allowed compressibility; when a penalty bulk modulus approach is adopted, like in the current work, increasing
\begin{figure}[htbp]
	\centering
   		\includegraphics[width=0.6\textwidth]{figures/ventricle_results} 
%	\subfigure[Predictions from the current work]
%	{
%   		\includegraphics[width=0.46\textwidth]{figures/ventricle_results} 
%   	}
%	\subfigure[\citet{Land2015} benchmarks]
%	{
%		\includegraphics[width=0.48\textwidth]{figures/ventricle_results_land2015}  
%	}
	\caption{Idealised ventricle: predictions for the four meshes from the present work overlaid on the round-robin predictions from \citet{Land2015}}
	\label{fig:ventricle_accuracy}
\end{figure}
